Bioverse: Potentially Observable Exoplanet Biosignature Patterns Under the UV Threshold Hypothesis for the Origin of Life

### 2025-03-25 src/tex/ms.tex
clarify that step-function f_life is only for the first step of OoL.

Presumably, not all habitable worlds are inhabited and not all inhabited worlds develop detectable biosignatures.
The fraction of \glspl{EEC} that are both inhabited and exhibit detectable biosignatures at the time of observation is unknown \rev{and is represented by the term $f_\mathrm{life}$.
This encompasses the probability of life both emerging and persisting to produce detectable biosignatures.}
\rev{Due to our ignorance about its true value or even its order of magnitude, we draw $f_\mathrm{life}$ from a log-uniform prior probability distribution} \revv{over the range $[10^{-15}, 1]$~\citep[][but see Appendix~\ref{sec:appendix-flife-prior} for a discussion of the impact of different priors]{Balbi2023a}}.
Let us consider the probability to detect a biosignature $P(L)$, and let our observable be the inferred past \gls{NUV} flux of the planet $F_\mathrm{NUV}$.
Under Hypothesis $H_1$, there exists a special unknown value of $F_\mathrm{NUV}$, noted $F_\mathrm{NUV, min}$ such that

\begin{align}
    P(L|F_\mathrm{NUV},H_1) &=  f_\mathrm{life} \quad \text{if } F_\mathrm{NUV}>F_\mathrm{NUV, min}\\
    P(L|F_\mathrm{NUV},H_1) &=  0               \quad  \text{otherwise}
\end{align}

where $f_\mathrm{life}$ is the unknown probability of abiogenesis.
The corresponding null hypothesis $H_\mathrm{null}$ is that there exists no such special value of $F_\mathrm{NUV}$ and that
\begin{equation}
P(L|F_\mathrm{NUV},H_\mathrm{null}) = f_\mathrm{life}.
\end{equation}
In other words, $H_\mathrm{null}$ states that $P(L)$ is independent of $F_\mathrm{NUV}$.

>>>>

Presumably, not all habitable worlds are inhabited and not all inhabited worlds develop detectable biosignatures.
The fraction of \glspl{EEC} that are both inhabited and exhibit detectable biosignatures at the time of observation is unknown \rev{and is represented by }\revv{ $f_\mathrm{life}$.}
\revv{This term captures the combined probability that life \textit{both} emerges on a planet and persists in a form that produces detectable biosignatures by the time of observation.
}
\rev{Due to our ignorance about its true value or even its order of magnitude, we draw $f_\mathrm{life}$ from a log-uniform prior probability distribution} \revv{over the range $[10^{-15}, 1]$~\citep[][but see Appendix~\ref{sec:appendix-flife-prior} for a discussion of the impact of different priors]{Balbi2023a}}.
Let us consider the probability to detect a biosignature $P(L)$, and let our observable be the inferred past \gls{NUV} flux of the planet $F_\mathrm{NUV}$.
Under Hypothesis $H_1$, there exists a special unknown value of $F_\mathrm{NUV}$, noted $F_\mathrm{NUV, min}$ such that

\begin{align}
    P(L|F_\mathrm{NUV},H_1) &=  f_\mathrm{life} \quad \text{if } F_\mathrm{NUV}>F_\mathrm{NUV, min}\\
    P(L|F_\mathrm{NUV},H_1) &=  0               \quad  \text{otherwise.}
\end{align}
\revv{Here, the step-function dependence on $F_\mathrm{NUV}$ applies only to the initial step of abiogenesis, consistent with the cyanosulfidic scenario in which UV irradiation is required for the synthesis of key prebiotic precursors.
We do not assume that the persistence of life or the presence of detectable biosignatures depends on UV flux.}

The corresponding null hypothesis $H_\mathrm{null}$ is that there exists no such special value of $F_\mathrm{NUV}$ and that
\begin{equation}
P(L|F_\mathrm{NUV},H_\mathrm{null}) = f_\mathrm{life}.
\end{equation}
In other words, $H_\mathrm{null}$ states that $P(L)$ is independent of $F_\mathrm{NUV}$.
